---
title: "Cycling_AD_GWAS_supp"
format: html
editor: visual
---

## Compile results from focused look at AD GWAS genes:

```{r}
library(tidyverse)
library(readxl)
```

What cutoffs to use for cycing in CTL?

```{r}
AmpRatioCutoff = 0.2
BHQCutoff = 0.1

AR_str = str_replace(toString(AmpRatioCutoff), "0\\.", "")
BHQ_str = str_replace(toString(BHQCutoff), "0\\.", "")
```

Read in results from focused look at GWAS in each cell types. I'm displaying the Rhythmic in CTL results.

```{r}

exc_ctl = read_xlsx("../Cyclops_ordering/downstream_output_Exc_all/AD_GWAS_diff_rhythms_CyclingBHQ1.xlsx", sheet = "GWAS_CTL_cycling") %>% dplyr::filter(amp_ratio >= AmpRatioCutoff & BHQ < BHQCutoff)

exc_ad = read_xlsx("../Cyclops_ordering/downstream_output_Exc_all/AD_GWAS_diff_rhythms_CyclingBHQ1.xlsx", sheet = "GWAS_AD_cycling") %>% dplyr::filter(amp_ratio >= AmpRatioCutoff & BHQ < BHQCutoff)

exc_dr = read_xlsx("../Cyclops_ordering/downstream_output_Exc_all/AD_GWAS_diff_rhythms_CyclingBHQ1.xlsx", sheet = "GWAS_diff_rhyth") %>% dplyr::filter(BHQ < BHQCutoff)

exc_dm = read_xlsx("../Cyclops_ordering/downstream_output_Exc_all/AD_GWAS_diff_rhythms_CyclingBHQ1.xlsx", sheet = "GWAS_diff_mesor")%>% dplyr::filter(BHQ < BHQCutoff)

exc_de = read_xlsx("../Cyclops_ordering/downstream_output_Exc_all/AD_GWAS_diff_rhythms_CyclingBHQ1.xlsx", sheet = "GWAS_diff_expr")%>% dplyr::filter(BHQ < BHQCutoff)

inh_ctl = read_xlsx("../Cyclops_ordering/downstream_output_Inhib_all/AD_GWAS_diff_rhythms_CyclingBHQ1.xlsx", sheet = "GWAS_CTL_cycling")%>% dplyr::filter(amp_ratio >= AmpRatioCutoff & BHQ < BHQCutoff)

inh_ad = read_xlsx("../Cyclops_ordering/downstream_output_Inhib_all/AD_GWAS_diff_rhythms_CyclingBHQ1.xlsx", sheet = "GWAS_AD_cycling")%>% dplyr::filter(amp_ratio >= AmpRatioCutoff & BHQ < BHQCutoff)

inh_dr = read_xlsx("../Cyclops_ordering/downstream_output_Inhib_all/AD_GWAS_diff_rhythms_CyclingBHQ1.xlsx", sheet = "GWAS_diff_rhyth") %>% dplyr::filter(BHQ < BHQCutoff)

inh_dm = read_xlsx("../Cyclops_ordering/downstream_output_Inhib_all/AD_GWAS_diff_rhythms_CyclingBHQ1.xlsx", sheet = "GWAS_diff_mesor") %>% dplyr::filter(BHQ < BHQCutoff)

inh_de = read_xlsx("../Cyclops_ordering/downstream_output_Inhib_all/AD_GWAS_diff_rhythms_CyclingBHQ1.xlsx", sheet = "GWAS_diff_expr") %>% dplyr::filter(BHQ < BHQCutoff)

mic_ctl = read_xlsx("../Cyclops_ordering/downstream_output_Mglia_all/AD_GWAS_diff_rhythms_CyclingBHQ1.xlsx", sheet = "GWAS_CTL_cycling")%>% dplyr::filter(amp_ratio >= AmpRatioCutoff & BHQ < BHQCutoff)

mic_ad = read_xlsx("../Cyclops_ordering/downstream_output_Mglia_all/AD_GWAS_diff_rhythms_CyclingBHQ1.xlsx", sheet = "GWAS_AD_cycling")%>% dplyr::filter(amp_ratio >= AmpRatioCutoff & BHQ < BHQCutoff)

mic_dr = read_xlsx("../Cyclops_ordering/downstream_output_Mglia_all/AD_GWAS_diff_rhythms_CyclingBHQ1.xlsx", sheet = "GWAS_diff_rhyth") %>% dplyr::filter(BHQ < BHQCutoff)

mic_dm = read_xlsx("../Cyclops_ordering/downstream_output_Mglia_all/AD_GWAS_diff_rhythms_CyclingBHQ1.xlsx", sheet = "GWAS_diff_mesor") %>% dplyr::filter(BHQ < BHQCutoff)

mic_de = read_xlsx("../Cyclops_ordering/downstream_output_Mglia_all/AD_GWAS_diff_rhythms_CyclingBHQ1.xlsx", sheet = "GWAS_diff_expr") %>% dplyr::filter(BHQ < BHQCutoff)

ast_ctl = read_xlsx("../Cyclops_ordering/downstream_output_Ast_all/AD_GWAS_diff_rhythms_CyclingBHQ1.xlsx", sheet = "GWAS_CTL_cycling")%>% dplyr::filter(amp_ratio >= AmpRatioCutoff & BHQ < BHQCutoff)

ast_ad = read_xlsx("../Cyclops_ordering/downstream_output_Ast_all/AD_GWAS_diff_rhythms_CyclingBHQ1.xlsx", sheet = "GWAS_AD_cycling")%>% dplyr::filter(amp_ratio >= AmpRatioCutoff & BHQ < BHQCutoff)

ast_dr = read_xlsx("../Cyclops_ordering/downstream_output_Ast_all/AD_GWAS_diff_rhythms_CyclingBHQ1.xlsx", sheet = "GWAS_diff_rhyth") %>% dplyr::filter(BHQ < BHQCutoff)

ast_dm = read_xlsx("../Cyclops_ordering/downstream_output_Ast_all/AD_GWAS_diff_rhythms_CyclingBHQ1.xlsx", sheet = "GWAS_diff_mesor") %>% dplyr::filter(BHQ < BHQCutoff)

ast_de = read_xlsx("../Cyclops_ordering/downstream_output_Ast_all/AD_GWAS_diff_rhythms_CyclingBHQ1.xlsx", sheet = "GWAS_diff_expr") %>% dplyr::filter(BHQ < BHQCutoff)
```

Define GWAS genes

```{r}
GWAS_genes = c("ABCA1", "ABCA7", "ABI3", "ACE", "ADAM17", "ADAMTS1", "ANK3", "ANKH", "APH1B", "APP", "BCKDK", "BIN1", "BLNK", "CASS4", "CD2AP",
"CLNK", "CLU", "COX7C", "CR1", "CTSB", "CTSH", "DOC2A", "EED", "EPDR1", "EPHA1", "FERMT2", "FOXF1", "GRN", "HLA-DQA1", "HS3ST5",
"ICA1", "IDUA", "IGH", "IL34", "INPP5D", "JAZF1", "KLF16", "LILRB2", "MAF", "MINDY2", "MME", "MS4A4A", "MYO15A", "NCK2", "PLCG2",
"PLEKHA1", "PRDM7", "PRKD3", "PTK2B", "RASGEF1C", "RBCK1", "RHOH", "SCIMP", "SEC61G", "SHARPIN", "SIGLEC11", "SLC24A4", "SLC2A4RG",
"SNX1", "SORL1", "SORT1", "SPDYE3", "SPI1", "SPPL2A", "TMEM106B", "TNIP1", "TPCN1", "TREM2", "TREML2", "TSPAN14", "TSPOAP1",
"UMAD1", "UNC5CL", "USP6NL", "WDR12", "WDR81", "WNT3")

GWAS_genes = c(c("APOE", "PSEN1", "PSEN2"), GWAS_genes)
```

Which GWAS genes are even possible to find in my dataset?

```{r}
all_symbols = read_csv("../normed_counts/Pseudobulk_all_FiltByExprDefault_TMM.csv", show_col_types = F) %>% dplyr::select(Gene_Symbols) %>% unname %>% unlist

#AD GWAS Symbols not possible to find:
GWAS_genes[which(!(GWAS_genes %in% all_symbols))]
```

Create Supplemental table, start with all AD GWAS genes in column "AD_genes"

```{r}

#TREML2 and IGH not in my rosmap data so I will exclude those:
GWAS_genes = setdiff(GWAS_genes, c("TREML2", "IGH"))

supp_table = data.frame(AD_genes = GWAS_genes,
                        #Exc
                        Exc_ctl = GWAS_genes %in% exc_ctl$Gene_Symbols,
                        Exc_ad = GWAS_genes %in% exc_ad$Gene_Symbols,
                        Exc_dr = GWAS_genes %in% exc_dr$Gene_Symbols,
                        Exc_dm = GWAS_genes %in% exc_dm$Gene_Symbols,
                        Exc_de = GWAS_genes %in% exc_de$`...1`,
                        #Inhib
                        Inh_ctl = GWAS_genes %in% inh_ctl$Gene_Symbols,
                        Inh_ad = GWAS_genes %in% inh_ad$Gene_Symbols,
                        Inh_dr = GWAS_genes %in% inh_dr$Gene_Symbols,
                        Inh_dm = GWAS_genes %in% inh_dm$Gene_Symbols,
                        Inh_de = GWAS_genes %in% inh_de$`...1`,
                        #Ast
                        Ast_ctl = GWAS_genes %in% ast_ctl$Gene_Symbols,
                        Ast_ad = GWAS_genes %in% ast_ad$Gene_Symbols,
                        Ast_dr = GWAS_genes %in% ast_dr$Gene_Symbols,
                        Ast_dm = GWAS_genes %in% ast_dm$Gene_Symbols,
                        Ast_de = GWAS_genes %in% ast_de$`...1`,
                        #Micro
                        Mic_ctl = GWAS_genes %in% mic_ctl$Gene_Symbols,
                        Mic_ad = GWAS_genes %in% mic_ad$Gene_Symbols,
                        Mic_dr = GWAS_genes %in% mic_dr$Gene_Symbols,
                        Mic_dm = GWAS_genes %in% mic_dm$Gene_Symbols,
                        Mic_de = GWAS_genes %in% mic_de$`...1`)

colSums(supp_table[,-1])
```

Replace Trues and Falses with "x":

```{r}
supp_table <- supp_table %>%
  mutate_all(~ ifelse(. == TRUE, "x", ifelse(. == FALSE, "", .)))
```

DE vs DM story:

```{r}
supp_table %>% select(grep("AD_genes|_dm$|_de$", colnames(supp_table))) %>% View
```

Just cycling:

```{r}
supp_table %>% select(grep("AD_genes|_ctl$|_ad$", colnames(supp_table))) %>% View
```

Diff rhythms:

```{r}
supp_table %>% select(grep("AD_genes|_dr$", colnames(supp_table))) %>% View
```

Exc only

```{r}
supp_table %>% select(grep("AD_genes|^Exc", colnames(supp_table))) %>% View
```

Write out Excel

```{r}
colnames(supp_table) = c("AD GWAS Genes",
                         "Excitatory Neurons cycling CTL",
                         "Excitatory Neurons cycling AD",
                         "Excitatory Neurons diff. rhyth.",
                         "Excitatory Neurons diff. mesor",
                         "Excitatory Neurons diff. expr.",
                         "Inhibitory Neurons cycling CTL",
                         "Inhibitory Neurons cycling AD",
                         "Inhibitory Neurons diff. rhyth.",
                         "Inhibitory Neurons diff. mesor",
                         "Inhibitory Neurons diff. expr",
                         "Astrocytes cycling CTL",
                         "Astrocytes cycling AD",
                         "Astrocytes diff. rhyth.",
                         "Astrocytes diff. mesor",
                         "Astrocytes diff. expr.",
                         "Microglia cycling CTL",
                         "Microglia cycling AD",
                         "Microglia diff. rhyth.",
                         "Microglia diff. mesor",
                         "Microglia diff. expr.")
library(writexl)
write_xlsx(supp_table, paste0("~/Desktop/Cycling_GWAS_AR",AR_str,"BHQ", BHQ_str, ".xlsx"), col_names = T)
```
